### 2019-02-14 sections/intuition.tex
fix wrong macro name
Changes to section 3.1 and 3.2

The central objective of tasks is to \emph{coordinate collaboration}.
Therefore \TOPHAT has combinators to express ways in which people can work together to reach a common goal.
Tasks can be executed after each other, at the same time, or conditionally.
This motivates the task combinators for steps, parallel combination, and choice.
One can say that tasks are a way to model \emph{workflows}.
% \TOPHAT is a language to specify workflows.

@@

\fixme{Extend}
Tasks are modular and composable,
can be abstracted over zero or more arguments,
arguments could themselves be tasks,
thus we have higher order workflows.

@@

A simple higher-order task which performs a task twice can be specified as follows.
\begin{TASK}
  let twice : Task $\tau$ -> Task $\tau$ = \t : Task $\tau$.
    t >>? \x : $\tau$. t
\end{TASK}
By using the step combinator $\When$ we specify that the given task \TS{t} should be performed a second time.
The result \TS{x} from the first run is ignored.

@@

>>>>

The central objective of \TOP is to \emph{coordinate collaboration}.
To this end, \TOPHAT has basic tasks called editors, whith which users can
interact, and combinators to express ways in which people can work together on
these tasks. Tasks can be executed after each other, at the same time, or
conditionally. This motivates the task combinators for steps, parallel
combination, and choice.
%One can say that tasks are a way to model \emph{workflows}.
% \TOPHAT is a language to specify workflows.

@@

Tasks are extremely flexible. They are modular; \fixme{why exactly?}. Tasks are
composable, using the aforementioned combinators. And tasks are higher order;
they can be abstracted over zero or more arguments, and those arguments could
be tasks themselves.

@@

A simple higher-order task which performs a task twice can be specified as
follows.
\begin{TASK}
  let twice : Task $\tau$ -> Task $\tau$ = \t : Task $\tau$. t >>? \x : $\tau$. t
\end{TASK}
By using the step combinator $\Next$ we specify that the given task \TS{t}
should be performed a second time. The result \TS{x} from the first run is
ignored.

@@

\fixme{conclude something about why this is convenient}
